---
title: "Thesis"
output: pdf_document
---

Libraries 
```{r}
library(readxl)
library(ggplot2)
library(gridExtra)
library(cowplot)
library(KMsurv)
library(survival)
library(MASS)
```


Reading in pathway to excel document that contains all injuries with statistics for each respective season
```{r}
injurydata=read_excel("C:\\Sammi\\Thesis\\Complete Injury Log with Stats.xlsx")
injurydata
```


Bar graphs for each position: point guard, shooting guard, small forward, power forward, center for each injury type: arm, back, finger, foot, hand, head, leg, toe, other

```{r}

par(mfrow=c(2,3))

# Bar graph for point guard position
pg<-data.frame(injury=c("Arm", "Back", "Finger", "Foot", "Hand", "Head", "Leg", "Toe", "Other"), frequency=c(18,25,10,63,6,6,128,
                                                            12,19))

pggraph<-ggplot(pg,aes(x=injury, y=frequency)) +
  geom_bar(stat="identity") +
  ylim(0,130) 

pggraph2<-print(pggraph + ggtitle("Point Guards"))


# Bar graph for shooting guard position
sg<-data.frame(injury=c("Arm", "Back", "Finger", "Foot", "Hand", "Head", "Leg", "Toe", "Other"), frequency=c(19,13,8,69,18,7,126,
                                                            8,16))

sggraph<-ggplot(sg,aes(x=injury, y=frequency)) +
  geom_bar(stat="identity") +
  ylim(0,130)

sggraph2<-print(sggraph + ggtitle("Shooting Guards"))

# Bar graph for small forward position
sf<-data.frame(injury=c("Arm", "Back", "Finger", "Foot", "Hand", "Head", "Leg", "Toe", "Other"), frequency=c(11,16,5,50,11,5,92,
                                                            11,12))

sfgraph<-ggplot(sf,aes(x=injury, y=frequency)) +
  geom_bar(stat="identity") +
  ylim(0,130)

sfgraph2<-print(sfgraph + ggtitle("Small Forwards"))

# Bar graph for power forward position
pf<-data.frame(injury=c("Arm", "Back", "Finger", "Foot", "Hand", "Head", "Leg", "Toe", "Other"), frequency=c(12,19,5,48,8,12,83,
                                                            9,17))

pfgraph<-ggplot(pf,aes(x=injury, y=frequency)) +
  geom_bar(stat="identity") +
  ylim(0,130)

pfgraph2<-print(pfgraph + ggtitle("Power Forwards"))

# Bar graph for center position
cen<-data.frame(injury=c("Arm", "Back", "Finger", "Foot", "Hand", "Head", "Leg", "Toe", "Other"), frequency=c(13,15,10,56,7,9,44,
                                                            2,18))

cengraph<-ggplot(cen,aes(x=injury, y=frequency)) +
  geom_bar(stat="identity") +
  ylim(0,130)

cengraph2<-print(cengraph + ggtitle("Centers"))

# bar graphs for all the pg, sg, sf, pf, cen
grid.arrange(pggraph,sggraph,sfgraph,pfgraph,cengraph, 
          ncol = 2, nrow = 3)
```

Box plots for each injury separated by the 5 positions
```{r}
# arm injury data
arm<-data.frame(injurydata[injurydata$Groupings=="Arm",])


# complete arm injury 
arm_complete<-arm[complete.cases(arm),]



# arm injury boxplot
ggplot(arm_complete, aes(x=Position, y=Days.on.IL, fill=Position)) + 
  geom_boxplot(alpha=0.3) +
  theme(legend.position="none")+
  ggtitle("Arm")+
  ylim(-3,45)


# back injury data
back<-data.frame(injurydata[injurydata$Groupings=="Back",])


# complete back injury 
back_complete<-back[complete.cases(back),]


# back injury boxplot
ggplot(back_complete, aes(x=Position, y=Days.on.IL, fill=Position)) + 
  geom_boxplot(alpha=0.3) +
  theme(legend.position="none")+
  ggtitle("Back")+
  ylim(-3,20)


# finger injury data
finger<-data.frame(injurydata[injurydata$Groupings=="Finger",])


# complete finger injury 
finger_complete<-finger[complete.cases(finger),]


# finger injury boxplot
ggplot(finger_complete, aes(x=Position, y=Days.on.IL, fill=Position)) + 
  geom_boxplot(alpha=0.3) +
  theme(legend.position="none")+
  ggtitle("Finger")+
  ylim(-3,40)


# foot injury data
foot<-data.frame(injurydata[injurydata$Groupings=="Foot",])

# complete foot injury 
foot_complete<-foot[complete.cases(foot),]


# foot injury boxplot
ggplot(foot_complete, aes(x=Position, y=Days.on.IL, fill=Position)) + 
  geom_boxplot(alpha=0.3) +
  theme(legend.position="none")+
  ggtitle("Foot")+
  ylim(-3,35)


# hand injury data
hand<-data.frame(injurydata[injurydata$Groupings=="Hand",])


# complete hand injury 
hand_complete<-hand[complete.cases(hand),]


# hand injury boxplot
ggplot(hand_complete, aes(x=Position, y=Days.on.IL, fill=Position)) + 
  geom_boxplot(alpha=0.3) +
  theme(legend.position="none")+
  ggtitle("Hand")+
  ylim(-3,40)


# head injury data
head<-data.frame(injurydata[injurydata$Groupings=="Head",])


# complete head injury 
head_complete<-head[complete.cases(head),]


# head injury boxplot
ggplot(head, aes(x=Position, y=Days.on.IL, fill=Position)) + 
  geom_boxplot(alpha=0.3) +
  theme(legend.position="none")+
  ggtitle("Head")+
  ylim(-3,15)


# leg injury data
leg<-data.frame(injurydata[injurydata$Groupings=="Leg",])


# complete leg injury 
leg_complete<-leg[complete.cases(leg),]


# leg injury boxplot
ggplot(leg_complete, aes(x=Position, y=Days.on.IL, fill=Position)) + 
  geom_boxplot(alpha=0.3) +
  theme(legend.position="none")+
  ggtitle("Leg")+
  ylim(0,30)


# toe injury data
toe<-data.frame(injurydata[injurydata$Groupings=="Toe",])

# complete toe injury 
toe_complete<-toe[complete.cases(toe),]


# toe injury boxplot
ggplot(toe_complete, aes(x=Position, y=Days.on.IL, fill=Position)) + 
  geom_boxplot(alpha=0.3) +
  theme(legend.position="none")+
  ggtitle("Toe")+
  ylim(-3,30)


# other injury data
other<-data.frame(injurydata[injurydata$Groupings=="Other",])


# complete other injury 
other_complete<-other[complete.cases(other),]


# other injury boxplot
ggplot(other_complete, aes(x=Position, y=Days.on.IL, fill=Position)) + 
  geom_boxplot(alpha=0.3) +
  theme(legend.position="none")+
  ggtitle("Other")+
  ylim(-3,15)
```

Mean age of player when an injury / a certain type of injury occurs
```{r}
# mean age of player with an injury overall in dataset
overall_mean<-mean(injurydata$Age,na.rm=TRUE)

# mean age of a player with arm injuries
arm_mean<-mean(arm$Age,na.rm=TRUE)
# less than overall mean

#mean age of a player with back injuries
back_mean<-mean(back$Age,na.rm=TRUE)
# less than overall mean

#mean age of a player with finger injuries
finger_mean<-mean(finger$Age,na.rm=TRUE)
# less than overall mean

#mean age of a player with foot injuries
foot_mean<-mean(foot$Age,na.rm=TRUE)
# less than overall mean

#mean age of a player with hand injuries
hand_mean<-mean(hand$Age,na.rm=TRUE)
# greater than overall mean

#mean age of a player with head injuries
head_mean<-mean(head$Age,na.rm=TRUE)
# less than overall mean

#mean age of a player with leg injuries
leg_mean<-mean(leg$Age,na.rm=TRUE)
# greater than overall mean

#mean age of a player with toe injuries
toe_mean<-mean(toe$Age,na.rm=TRUE)
# less than overall mean

#mean age of a player with other injuries
other_mean<-mean(other$Age,na.rm=TRUE)
# less than overall mean

# Putting into a table
mean_data<-matrix(c(overall_mean,arm_mean,back_mean,finger_mean,foot_mean,hand_mean,
head_mean,leg_mean,toe_mean,other_mean),ncol=1,byrow=TRUE)
mean_data
# specify the column names and row names of matrix
colnames(mean_data)<-c("Mean")
rownames(mean_data)<-c("Overall","Arm","Back","Finger","Foot","Hand","Head","Leg","Toe","Other")
# assign to table
mean_table=as.table(mean_data)
knitr::kable(mean_table)
```


Acute injuries are common in those elderly people participating in sport activities which demand high coordination, reaction time, and balance capabilities, such as ball games, down-hill skiing, and gymnastics. Muscle has been reported to be the most commonly acutelyinjured tissue among active elderly athletes. The lower extremities are the most susceptible to injury. 


```{r}

# Correlation between season statistics for players with all injuries
cor(injurydata[19:35],use="na.or.complete")

# Correlation between days on the IL with season statistics for players with all injuries
cor(injurydata[19:35],use="na.or.complete",injurydata$`Days on IL`)

# Correlation between season statistics for players with arm injuries
cor(arm_complete[19:35])

# Correlation between days on the IL with season statistics for players with arm injuries
cor(arm_complete[19:35],arm_complete$Days.on.IL)

# Correlation between season statistics for players with back injuries
cor(back_complete[19:35])

# Correlation between days on the IL with season statistics for players with back injuries
cor(back_complete[19:35],back_complete$Days.on.IL)

# Correlation between season statistics for players with finger injuries
cor(finger_complete[19:35])

# Correlation between days on the IL with season statistics for players with finger injuries
cor(finger_complete[19:35],finger_complete$Days.on.IL)

# Correlation between season statistics for players with foot injuries
cor(foot_complete[19:35])

# Correlation between days on the IL with season statistics for players with foot injuries
cor(foot_complete[19:35],foot_complete$Days.on.IL)

# Correlation between season statistics for players with hand injuries
cor(hand_complete[19:35])

# Correlation between days on the IL with season statistics for players with hand injuries
cor(hand_complete[19:35],hand_complete$Days.on.IL)

# Correlation between season statistics for players with head injuries
cor(head_complete[19:35])

# Correlation between days on the IL with season statistics for players with head injuries
cor(head_complete[19:35],head_complete$Days.on.IL)

# Correlation between season statistics for players with leg injuries
cor(leg_complete[19:35])

# Correlation between days on the IL with season statistics for players with leg injuries
cor(leg_complete[19:35],leg_complete$Days.on.IL)

# Correlation between season statistics for players with toes injuries
cor(toe_complete[19:35])

# Correlation between days on the IL with season statistics for players with toe injuries
cor(toe_complete[19:35],toe_complete$Days.on.IL)

# Correlation between season statistics for players with other injuries
cor(other_complete[19:35])

# Correlation between days on the IL with season statistics for players with other injuries
cor(other_complete[19:35],other_complete$Days.on.IL)

```




Question: On average, how many times is a player put on the injury list given that they have played at least 5 seasons in the range 2011-2020?
```{r}
number_of_rows<-nrow(injurydata)

# Total number of injured players in dataset is 241

number_of_players<-241

# Average number of injuries per player
avginjury<-number_of_rows/number_of_players
avginjury
```
The average player is put on the injury list 7.8 times


Question: What is the probability that a player has the same injury more than once?

(No calculations done here -- setting up data sets into tables and data frames)
```{r}

# First time injuries as a table
arm_first_injury<-table(injurydata$Groupings=="Arm"&injurydata$`Frequency of Injury`=="1")
back_first_injury<-table(injurydata$Groupings=="Back"&injurydata$`Frequency of Injury`=="1")
finger_first_injury<-table(injurydata$Groupings=="Finger"&injurydata$`Frequency of Injury`=="1")
foot_first_injury<-table(injurydata$Groupings=="Foot"&injurydata$`Frequency of Injury`=="1")
hand_first_injury<-table(injurydata$Groupings=="Hand"&injurydata$`Frequency of Injury`=="1")
head_first_injury<-table(injurydata$Groupings=="Head"&injurydata$`Frequency of Injury`=="1")
leg_first_injury<-table(injurydata$Groupings=="Leg"&injurydata$`Frequency of Injury`=="1")
toe_first_injury<-table(injurydata$Groupings=="Toe"&injurydata$`Frequency of Injury`=="1")
other_first_injury<-table(injurydata$Groupings=="Other"&injurydata$`Frequency of Injury`=="1")

# Total injuries as a table

total_arm_injuries<-table(injurydata$Groupings=="Arm")
total_back_injuries<-table(injurydata$Groupings=="Back")
total_finger_injuries<-table(injurydata$Groupings=="Finger")
total_foot_injuries<-table(injurydata$Groupings=="Foot")
total_hand_injuries<-table(injurydata$Groupings=="Hand")
total_head_injuries<-table(injurydata$Groupings=="Head")
total_leg_injuries<-table(injurydata$Groupings=="Leg")
total_toe_injuries<-table(injurydata$Groupings=="Toe")
total_other_injuries<-table(injurydata$Groupings=="Other")


# Second time injuries as a table

arm_sec_injury<-table(injurydata$Groupings=="Arm"&injurydata$`Frequency of Injury`=="2")
back_sec_injury<-table(injurydata$Groupings=="Back"&injurydata$`Frequency of Injury`=="2")
finger_sec_injury<-table(injurydata$Groupings=="Finger"&injurydata$`Frequency of Injury`=="2")
foot_sec_injury<-table(injurydata$Groupings=="Foot"&injurydata$`Frequency of Injury`=="2")
hand_sec_injury<-table(injurydata$Groupings=="Hand"&injurydata$`Frequency of Injury`=="2")
head_sec_injury<-table(injurydata$Groupings=="Head"&injurydata$`Frequency of Injury`=="2")
leg_sec_injury<-table(injurydata$Groupings=="Leg"&injurydata$`Frequency of Injury`=="2")
toe_sec_injury<-table(injurydata$Groupings=="Toe"&injurydata$`Frequency of Injury`=="2")
other_sec_injury<-table(injurydata$Groupings=="Other"&injurydata$`Frequency of Injury`=="2")
```

```{r}
# First injury for each grouping -- transforming contingency table into a data frame 
# so that I am able to extract the TRUE column out of the contingency table

# Arm
arm_first_injury_df<-as.data.frame(arm_first_injury)
arm_first_injury_df_TRUE<-arm_first_injury_df[2,2]
arm_first_injury_df_TRUE

# Back
back_first_injury_df<-as.data.frame(back_first_injury)
back_first_injury_df_TRUE<-back_first_injury_df[2,2]
back_first_injury_df_TRUE

# Finger
finger_first_injury_df<-as.data.frame(finger_first_injury)
finger_first_injury_df_TRUE<-finger_first_injury_df[2,2]
finger_first_injury_df_TRUE

# Foot
foot_first_injury_df<-as.data.frame(foot_first_injury)
foot_first_injury_df_TRUE<-foot_first_injury_df[2,2]
foot_first_injury_df_TRUE

# Hand
hand_first_injury_df<-as.data.frame(hand_first_injury)
hand_first_injury_df_TRUE<-hand_first_injury_df[2,2]
hand_first_injury_df_TRUE

# Head
head_first_injury_df<-as.data.frame(head_first_injury)
head_first_injury_df_TRUE<-head_first_injury_df[2,2]
head_first_injury_df_TRUE

# Leg
leg_first_injury_df<-as.data.frame(leg_first_injury)
leg_first_injury_df_TRUE<-leg_first_injury_df[2,2]
leg_first_injury_df_TRUE

# Toe
toe_first_injury_df<-as.data.frame(toe_first_injury)
toe_first_injury_df_TRUE<-toe_first_injury_df[2,2]
toe_first_injury_df_TRUE

# Other
other_first_injury_df<-as.data.frame(other_first_injury)
other_first_injury_df_TRUE<-other_first_injury_df[2,2]
other_first_injury_df_TRUE


# Putting into a table
first_injury<-matrix(c(arm_first_injury_df_TRUE,back_first_injury_df_TRUE,finger_first_injury_df_TRUE,foot_first_injury_df_TRUE,hand_first_injury_df_TRUE,head_first_injury_df_TRUE,leg_first_injury_df_TRUE,toe_first_injury_df_TRUE,other_first_injury_df_TRUE),ncol=1,byrow=TRUE)

# specify the column names and row names of matrix
colnames(first_injury)<-c("Number of First Injuries")
rownames(first_injury)<-c("Arm","Back","Finger","Foot","Hand","Head","Leg","Toe","Other")
# assign to table
first_injury_table=as.table(first_injury)
knitr::kable(first_injury_table)


# Total number of injuries -- transforming contingency table into a data frame 
# so that I am able to extract the TRUE column out of the contingency table

# arm
total_arm_injuries_df<-as.data.frame(total_arm_injuries)
total_arm_injuries_df_TRUE<-total_arm_injuries_df[2,2]
total_arm_injuries_df_TRUE

# back
total_back_injuries_df<-as.data.frame(total_back_injuries)
total_back_injuries_df_TRUE<-total_back_injuries_df[2,2]
total_back_injuries_df_TRUE

# finger
total_finger_injuries_df<-as.data.frame(total_finger_injuries)
total_finger_injuries_df_TRUE<-total_finger_injuries_df[2,2]
total_finger_injuries_df_TRUE

# foot
total_foot_injuries_df<-as.data.frame(total_foot_injuries)
total_foot_injuries_df_TRUE<-total_foot_injuries_df[2,2]
total_foot_injuries_df_TRUE

# Hand
total_hand_injuries_df<-as.data.frame(total_hand_injuries)
total_hand_injuries_df_TRUE<-total_hand_injuries_df[2,2]
total_hand_injuries_df_TRUE

# Head
total_head_injuries_df<-as.data.frame(total_head_injuries)
total_head_injuries_df_TRUE<-total_head_injuries_df[2,2]
total_head_injuries_df_TRUE

# Leg
total_leg_injuries_df<-as.data.frame(total_leg_injuries)
total_leg_injuries_df_TRUE<-total_leg_injuries_df[2,2]
total_leg_injuries_df_TRUE

# Toe
total_toe_injuries_df<-as.data.frame(total_toe_injuries)
total_toe_injuries_df_TRUE<-total_toe_injuries_df[2,2]
total_toe_injuries_df_TRUE

# Other
total_other_injuries_df<-as.data.frame(total_other_injuries)
total_other_injuries_df_TRUE<-total_other_injuries_df[2,2]
total_other_injuries_df_TRUE

table(total_arm_injuries_df_TRUE,total_back_injuries_df_TRUE)

# Putting into a table
total_injury<-matrix(c(total_arm_injuries_df_TRUE,total_back_injuries_df_TRUE,total_finger_injuries_df_TRUE,total_foot_injuries_df_TRUE,total_hand_injuries_df_TRUE,total_head_injuries_df_TRUE,total_leg_injuries_df_TRUE,total_toe_injuries_df_TRUE,total_other_injuries_df_TRUE),ncol=1,byrow=TRUE)

# specify the column names and row names of matrix
colnames(total_injury)<-c("Number of Total Injuries")
rownames(total_injury)<-c("Arm","Back","Finger","Foot","Hand","Head","Leg","Toe","Other")
# assign to table
total_injury_table=as.table(total_injury)
knitr::kable(total_injury_table)

# Second injury for each grouping -- transforming contingency table into a data frame 
# so that I am able to extract the TRUE column out of the contingency table

# Arm
arm_sec_injury_df<-as.data.frame(arm_sec_injury)
arm_sec_injury_df_TRUE<-arm_sec_injury_df[2,2]
arm_sec_injury_df_TRUE

# Back
back_sec_injury_df<-as.data.frame(back_sec_injury)
back_sec_injury_df_TRUE<-back_sec_injury_df[2,2]
back_sec_injury_df_TRUE

# Finger
finger_sec_injury_df<-as.data.frame(finger_sec_injury)
finger_sec_injury_df_TRUE<-finger_sec_injury_df[2,2]
finger_sec_injury_df_TRUE

# Foot
foot_sec_injury_df<-as.data.frame(foot_sec_injury)
foot_sec_injury_df_TRUE<-foot_sec_injury_df[2,2]
foot_sec_injury_df_TRUE

# Hand
hand_sec_injury_df<-as.data.frame(hand_sec_injury)
hand_sec_injury_df_TRUE<-hand_sec_injury_df[2,2]
hand_sec_injury_df_TRUE

# Head
head_sec_injury_df<-as.data.frame(head_sec_injury)
head_sec_injury_df_TRUE<-head_sec_injury_df[2,2]
head_sec_injury_df_TRUE

# Leg
leg_sec_injury_df<-as.data.frame(leg_sec_injury)
leg_sec_injury_df_TRUE<-leg_sec_injury_df[2,2]
leg_sec_injury_df_TRUE

# Toe
toe_sec_injury_df<-as.data.frame(toe_sec_injury)
toe_sec_injury_df_TRUE<-toe_sec_injury_df[2,2]
toe_sec_injury_df_TRUE

# Other
other_sec_injury_df<-as.data.frame(other_sec_injury)
other_sec_injury_df_TRUE<-other_sec_injury_df[2,2]
other_sec_injury_df_TRUE

# Putting into a table
sec_injury<-matrix(c(arm_sec_injury_df_TRUE,back_sec_injury_df_TRUE,finger_sec_injury_df_TRUE,foot_sec_injury_df_TRUE,hand_sec_injury_df_TRUE,head_sec_injury_df_TRUE,leg_sec_injury_df_TRUE,toe_sec_injury_df_TRUE,other_sec_injury_df_TRUE),ncol=1,byrow=TRUE)

# specify the column names and row names of matrix
colnames(sec_injury)<-c("Number of Second Injuries")
rownames(sec_injury)<-c("Arm","Back","Finger","Foot","Hand","Head","Leg","Toe","Other")
# assign to table
sec_injury_table=as.table(sec_injury)
knitr::kable(sec_injury_table)

```

Given that you have had an injury, what is the probability that it is the first injury of this grouping type?
```{r}
prob_first<-first_injury_table/total_injury_table
colnames(prob_first)<-"Probability of First Injury"
prob_first

# specify the column names and row names of matrix
colnames(prob_first)<-c("Probability of First Injury")
rownames(prob_first)<-c("Arm","Back","Finger","Foot","Hand","Head","Leg","Toe","Other")
# assign to table
prob_first_table=as.table(prob_first)
knitr::kable(prob_first_table)
```
A hand injury has the highest probability that it is the first injury and a leg injury has the lowest probability that it is the first injury. This makes sense because one would expect there to be the most leg injuries in basketball since injured ACLs are one of the most common injuries. On the other hand, hand injuries are in the running for the least common injuries. 


Given that you have had an injury, what is the probability that it is the second injury of this grouping type?
```{r}
prob_sec<-sec_injury_table/total_injury_table
colnames(prob_sec)<-"Probability of Second Injury"
prob_sec
```


(total injury - first time injury) / total injury = probability of same injury reoccurring

Given that you have had one particular injury, what is the probability of having the same injury?
```{r}
# reinjure arm
reinjure_arm<-(total_arm_injuries_df_TRUE - arm_first_injury_df_TRUE) / total_arm_injuries_df_TRUE
reinjure_arm

# reinjure back
reinjure_back<-(total_back_injuries_df_TRUE - back_first_injury_df_TRUE) / total_back_injuries_df_TRUE
reinjure_back

# reinjure finger
reinjure_finger<-(total_finger_injuries_df_TRUE - finger_first_injury_df_TRUE) / total_finger_injuries_df_TRUE
reinjure_finger

# reinjure foot
reinjure_foot<-(total_foot_injuries_df_TRUE - foot_first_injury_df_TRUE) / total_foot_injuries_df_TRUE
reinjure_foot

# reinjure hand
reinjure_hand<-(total_hand_injuries_df_TRUE - hand_first_injury_df_TRUE) / total_hand_injuries_df_TRUE
reinjure_hand

# reinjure head
reinjure_head<-(total_head_injuries_df_TRUE - head_first_injury_df_TRUE) / total_head_injuries_df_TRUE
reinjure_head

# reinjure leg
reinjure_leg<-(total_leg_injuries_df_TRUE - leg_first_injury_df_TRUE) / total_leg_injuries_df_TRUE
reinjure_leg

# reinjure toe
reinjure_toe<-(total_toe_injuries_df_TRUE - toe_first_injury_df_TRUE) / total_toe_injuries_df_TRUE
reinjure_toe

# reinjure other
reinjure_other<-(total_other_injuries_df_TRUE - other_first_injury_df_TRUE) / total_other_injuries_df_TRUE
reinjure_other

# Putting into a table
reinjure<-matrix(c(reinjure_arm,reinjure_back,reinjure_finger,reinjure_foot,reinjure_hand,reinjure_head,reinjure_leg,reinjure_toe,reinjure_other),ncol=1,byrow=TRUE)

# specify the column names and row names of matrix
colnames(reinjure)<-c("Reinjure Probability")
rownames(reinjure)<-c("Arm","Back","Finger","Foot","Hand","Head","Leg","Toe","Other")
# assign to table
reinjure_table=as.table(reinjure)
knitr::kable(reinjure_table)
```
Leg injuries have the highest probability of reinjure which makes sense since this grouping has the overall highest injury rate. Hand injuries have the lowest probability of reinjure which makes sense since this grouping has one of the lowest injury rates. 





