---
title: "Thesis_Scratch2"
output: pdf_document
date: "2023-03-07"
---

Used a Cox proportional hazard model (coxph) to model the relationship between days on the injury list and the age of the player when the injury occurred, the player's height, the player's weight, and the cumulative minutes the player played during the regular season. 

Censory indicator -- 1 if event is censored vs 0 if event is uncensored

Libraries 
```{r}
library(readxl)
library(ggplot2)
library(gridExtra)
library(cowplot)
library(KMsurv)
library(survival)
library(MASS)
```

Reading in pathway to excel document that contains all injuries with statistics for each respective season
```{r}
injurydata=read_excel("C:\\Sammi\\Thesis\\Complete Injury Log with Stats.xlsx")
```


Season 1
```{r}
# subsetting to only data in the first season
first_season<-subset(injurydata,injurydata$Season=="2011-2012")
first_season

# creating a dummy variable for censory indicator
z1=ifelse(first_season$`Censored Indicator`=="1",1,0)
z1

season_1<-coxph(Surv(first_season$`Minutes Before Injury`,z1)~first_season$FGA+first_season$FTA+first_season$REB
+first_season$`Number of Seasons Played`+first_season$FGM+first_season$FTM+
first_season$FTA+first_season$TOV+first_season$PF+first_season$AST
+first_season$STL+first_season$BLK+first_season$PTS+first_season$`Height cm`
+first_season$Weight+first_season$`3PA`+(first_season$`3PA`*first_season$Position)+(first_season$Age*first_season$PTS)+(first_season$Age*first_season$Position)
,data=first_season)
fit1<-stepAIC(season_1,direction="both",k=2)

summary(season_1)

#plotting survival curve for injury occurring in the first season
survival_curve1=plot(survfit(season_1), ylim=c(0,1),xlim=c(0,1500),main="Survival Curve Season 1",xlab="Years",ylab="Survival Probability")
survival_curve1

# Cox-Residuals for assessing model fit
# If the model is not a good fit, this could be because of outliers
coxres_1<-season_1$y[,2]-residuals(season_1)
coxres_season1<-survfit(Surv(coxres_1,season_1$y[,2])~1)
plot(coxres_season1,fun="cumhaz",bty="n",lwd=2,las=1,xlim=c(0,1.2),ylim=c(0,1.5),main="Cox-Residuals Season 1",xlab="Residual", ylab="Cumulative hazard")
abline(0, 1, col="red", lwd=2)


# Martingale Residuals
plot(season_1$linear.predictors,residuals(season_1),ylim=c(-2,2),pch=19,las=1, bty="n",col=5:6,main="Martingale Residuals Season 1",xlab="Prognostic Index", ylab="Martingale Residual")
abline(0,0,lty=2,lwd=2)
legend("bottomleft", c("Censored","Failures"),cex=0.8,col=5:6,pch=19)

```

Season 2
```{r}
# subsetting to only data in the second season
second_season<-subset(injurydata,injurydata$Season=="2012-2013")
second_season

# creating a dummy variable for censory indicator
z2=ifelse(second_season$`Censored Indicator`=="1",1,0)
z2

season_2<-coxph(Surv(second_season$`Minutes Before Injury`,z2)~second_season$FGA+second_season$FTA+second_season$REB
+second_season$`Number of Seasons Played`+second_season$FGM+second_season$FTM+
second_season$FTA+second_season$TOV+second_season$PF+second_season$AST
+second_season$STL+second_season$BLK+second_season$PTS+second_season$`Height cm`
+second_season$Weight+second_season$`3PA`+(second_season$`3PA`*second_season$Position)+(second_season$Age*second_season$PTS)+(second_season$Age*second_season$Position)
,data=second_season)
fit2<-stepAIC(season_2,direction="both",k=2)

season_2

summary(season_2)

#plotting survival curve for injury occurring in the second season
plot(survfit(season_2))

# Cox-Residuals for assessing model fit
coxres_2<-season_2$y[,2]-residuals(season_2)
coxres_season2<-survfit(Surv(coxres_2,season_2$y[,2])~1)
plot(coxres_season2,fun="cumhaz",bty="n",lwd=2, las=1,xlim=c(0,1.2),ylim=c(0,1.5),
     xlab="Residual", ylab="Cumulative hazard")
abline(0, 1, col="red", lwd=2)

# Martingale Residuals
plot(season_2$linear.predictors,residuals(season_2),ylim=c(-2,2),pch=19,las=1, bty="n", col=5:6,main="Martingale Residuals Season 2",xlab="Prognostic Index", ylab="Martingale Residual")
abline(0,0,lty=2,lwd=2)
legend("bottomleft", c("Censored","Failures"),cex=0.8,col=5:6,pch=19)

```

Season 3
```{r}
# subsetting to only data in the third season
third_season<-subset(injurydata,injurydata$Season=="2013-2014")
third_season

# creating a dummy variable for censory indicator
z3=ifelse(third_season$`Censored Indicator`=="1",1,0)
z3

# running stepwise function on all covariates in third season
season_3<-coxph(Surv(third_season$`Minutes Before Injury`,z3)~third_season$FGA+third_season$FTA+third_season$REB
+third_season$`Number of Seasons Played`+third_season$FGM+third_season$FTM+
third_season$FTA+third_season$TOV+third_season$PF+third_season$AST
+third_season$STL+third_season$BLK+third_season$PTS+third_season$`Height cm`
+third_season$Weight+third_season$`3PA`+(third_season$`3PA`*third_season$Position)+(third_season$Age*third_season$PTS)+(third_season$Age*third_season$Position)
,data=third_season)
fit3<-stepAIC(season_3,direction="both",k=2)

summary(season_3)

#plotting survival curve for injury occurring in the third season
survival_curve3<-plot(survfit(season_3),main="Survival Curve Season 3",xlab="Time",ylab="Survival Probability")
survival_curve3

# Cox-Residuals for assessing model fit
coxres_3<-season_3$y[,2]-residuals(season_3)
coxres_season3<-survfit(Surv(coxres_3,season_3$y[,2])~1)
plot(coxres_season3,fun="cumhaz",bty="n",lwd=2,las=1,xlim=c(0,1.2),ylim=c(0,1.5),main="Cox-Residuals Season 3",xlab="Residual", ylab="Cumulative hazard")
abline(0, 1, col="red", lwd=2)



# Martingale Residuals
plot(season_3$linear.predictors,residuals(season_3),ylim=c(-2,2),pch=19,las=1, bty="n",col=5:6,main="Martingale Residuals Season 3",xlab="Prognostic Index", ylab="Martingale Residual")
abline(0,0,lty=2,lwd=2)
legend("bottomleft", c("Censored","Failures"),cex=0.8,col=5:6,pch=19)
 
```
Season 4
```{r}
# subsetting to only data in the fourth season
fourth_season<-subset(injurydata,injurydata$Season=="2014-2015")
fourth_season

# creating a dummy variable for censory indicator
z4=ifelse(fourth_season$`Censored Indicator`=="1",1,0)
z4

# running stepwise function on all covariates in fourth season
season_4<-coxph(Surv(fourth_season$`Minutes Before Injury`,z4)~fourth_season$FGA+fourth_season$FTA+fourth_season$REB
+fourth_season$`Number of Seasons Played`+fourth_season$FGM+fourth_season$FTM+
fourth_season$FTA+fourth_season$TOV+fourth_season$PF+fourth_season$AST
+fourth_season$STL+fourth_season$BLK+fourth_season$PTS+fourth_season$`Height cm`
+fourth_season$Weight+fourth_season$`3PA`+(fourth_season$`3PA`*fourth_season$Position)+(fourth_season$Age*fourth_season$PTS)+(fourth_season$Age*fourth_season$Position)
,data=fourth_season)
fit4<-stepAIC(season_4,direction="both",k=2)

summary(season_4)

#plotting survival curve for injury occurring in the fourth season
survival_curve4<-plot(survfit(season_4),main="Survival Curve Season 4",xlab = "Time",ylab="Survival Probability")
survival_curve4

# Cox-Residuals for assessing model fit
coxres_4<-season_4$y[,2]-residuals(season_4)
coxres_season4<-survfit(Surv(coxres_4,season_4$y[,2])~1)
plot(coxres_season4,fun="cumhaz",bty="n",lwd=2,las=1,xlim=c(0,2),main="Cox-Residuals Season 4",xlab="Residual", ylab="Cumulative hazard")
abline(0, 1, col="red", lwd=2)


# Martingale Residuals
plot(season_4$linear.predictors,residuals(season_4),ylim=c(-2,2),pch=19,las=1, bty="n",col=5:6,main="Martingale Residuals Season 4",xlab="Prognostic Index", ylab="Martingale Residual")
abline(0,0,lty=2,lwd=2)
legend("bottomleft", c("Censored","Failures"),cex=0.8,col=5:6,pch=19)
```
Season 5
```{r}
# subsetting to only data in the fifth season
fifth_season<-subset(injurydata,injurydata$Season=="2015-2016")
fifth_season

# creating a dummy variable for censory indicator
z5=ifelse(fifth_season$`Censored Indicator`=="1",1,0)
z5

# running stepwise function on all covariates in fifth season
season_5<-coxph(Surv(fifth_season$`Minutes Before Injury`,z5)~fifth_season$FGA+fifth_season$FTA+fifth_season$REB
+fifth_season$`Number of Seasons Played`+fifth_season$FGM+fifth_season$FTM+
  fifth_season$FTA+fifth_season$TOV+fifth_season$PF+fifth_season$AST
+fifth_season$STL+fifth_season$BLK+fifth_season$PTS+fifth_season$`Height cm`
+fifth_season$Weight+fifth_season$`3PA`+(fifth_season$`3PA`*fifth_season$Position)+(fifth_season$Age*fifth_season$PTS)+(fifth_season$Age*fifth_season$Position)
,data=fifth_season)
fit5<-stepAIC(season_5,direction="both",k=2)

summary(season_5)

#plotting survival curve for injury occurring in the fifth season
survival_curve5<-plot(survfit(season_5), ylim=c(0,1),main="Survival Curve Season 5")
survival_curve5

# Cox-Residuals for assessing model fit
coxres_5<-season_5$y[,2]-residuals(season_5)
coxres_season5<-survfit(Surv(coxres_5,season_5$y[,2])~1)
plot(coxres_season5,fun="cumhaz",bty="n",lwd=2,las=1,xlim=c(0,1.2),ylim=c(0,1.5), main="Cox-Residuals Season 5",xlab="Residual", ylab="Cumulative hazard")
abline(0, 1, col="red", lwd=2)


# Martingale Residuals
plot(season_5$linear.predictors,residuals(season_5),ylim=c(-2,2),pch=19,las=1, bty="n",col=5:6,main="Martingale Residuals Season 5",xlab="Prognostic Index", ylab="Martingale Residual")
abline(0,0,lty=2,lwd=2)
legend("bottomleft", c("Censored","Failures"),cex=0.8,col=5:6,pch=19)

```

Season 6
```{r}
# subsetting to only data in the sixth season
sixth_season<-subset(injurydata,injurydata$Season=="2016-2017")
sixth_season

# creating a dummy variable for censory indicator
z6=ifelse(sixth_season$`Censored Indicator`=="1",1,0)
z6

# running stepwise function on all covariates in sixth season
season_6<-coxph(Surv(sixth_season$`Minutes Before Injury`,z6)~sixth_season$FGA+sixth_season$FTA+sixth_season$REB
+sixth_season$`Number of Seasons Played`+sixth_season$FGM+sixth_season$FTM+
sixth_season$FTA+sixth_season$TOV+sixth_season$PF+sixth_season$AST
+sixth_season$STL+sixth_season$BLK+sixth_season$PTS+sixth_season$`Height cm`
+sixth_season$Weight+sixth_season$`3PA`+(sixth_season$`3PA`*sixth_season$Position)+(sixth_season$Age*sixth_season$PTS)+(sixth_season$Age*sixth_season$Position)
,data=sixth_season)
fit6<-stepAIC(season_6,direction="both",k=2)
summary(season_6)

#plotting survival curve for injury occurring in the sixth season
survival_curve6<-plot(survfit(season_6),ylim=c(0,1),main="Survival Curve Season 6")
survival_curve6

# Cox-Residuals for assessing model fit
coxres_6<-season_6$y[,2]-residuals(season_6)
coxres_season6<-survfit(Surv(coxres_6,season_6$y[,2])~1)
plot(coxres_season6,fun="cumhaz",bty="n",lwd=2,las=1,xlim=c(0,6),main="Cox-Residuals Season 6",xlab="Residual", ylab="Cumulative hazard")
abline(0, 1, col="red", lwd=2)


# Martingale Residuals
plot(season_6$linear.predictors,residuals(season_6),ylim=c(-2,2),pch=19,las=1, bty="n",col=5:6,main="Martingale Residuals Season 6",xlab="Prognostic Index", ylab="Martingale Residual")
abline(0,0,lty=2,lwd=2)
legend("bottomleft", c("Censored","Failures"),cex=0.8,col=5:6,pch=19)
```
Season 7
```{r}
# subsetting to only data in the seventh season
seventh_season<-subset(injurydata,injurydata$Season=="2017-2018")
seventh_season

# creating a dummy variable for censory indicator
z7=ifelse(seventh_season$`Censored Indicator`=="1",1,0)
z7

# running stepwise function on all covariates in seventh season
season_7<-coxph(Surv(seventh_season$`Minutes Before Injury`,z7)~seventh_season$FGA+seventh_season$FTA+seventh_season$REB
+seventh_season$`Number of Seasons Played`+seventh_season$FGM+seventh_season$FTM+
seventh_season$FTA+seventh_season$TOV+seventh_season$PF+seventh_season$AST
+seventh_season$STL+seventh_season$BLK+seventh_season$PTS+seventh_season$`Height cm`
+seventh_season$Weight+seventh_season$`3PA`+(seventh_season$`3PA`*seventh_season$Position)+(seventh_season$Age*seventh_season$PTS)+(seventh_season$Age*seventh_season$Position)
,data=seventh_season)
fit7<-stepAIC(season_7,direction="both",k=2)

summary(season_7)


# Cox-Residuals for assessing model fit
coxres_7<-season_7$y[,2]-residuals(season_7)
coxres_season7<-survfit(Surv(coxres_7,season_7$y[,2])~1)
plot(coxres_season7,fun="cumhaz",bty="n",lwd=2,las=1,xlim=c(0,1),ylim=c(0,1.5),main="Cox-Residuals Season 7",xlab="Residual", ylab="Cumulative hazard")
abline(0, 1, col="red", lwd=2)

# Martingale Residuals
plot(season_7$linear.predictors,residuals(season_7),ylim=c(-2,2),pch=19,las=1, bty="n",col=5:6,main="Martingale Residuals Season 7",xlab="Time", ylab="Martingale Residual")
abline(0,0,lty=2,lwd=2)
legend("bottomleft", c("Censored","Failures"),cex=0.8,col=5:6,pch=19)
```

Season 8
```{r}
# subsetting to only data in the eighth season
eighth_season<-subset(injurydata,injurydata$Season=="2018-2019")
eighth_season

# creating a dummy variable for censory indicator
z8=ifelse(eighth_season$`Censored Indicator`=="1",1,0)
z8

# running stepwise function on all covariates in eighth season
season_8<-coxph(Surv(eighth_season$`Minutes Before Injury`,z8)~eighth_season$FGA+eighth_season$FTA+eighth_season$REB
+eighth_season$`Number of Seasons Played`+eighth_season$FGM+eighth_season$FTM+
eighth_season$FTA+eighth_season$TOV+eighth_season$PF+eighth_season$AST
+eighth_season$STL+eighth_season$BLK+eighth_season$PTS+eighth_season$`Height cm`
+eighth_season$Weight+eighth_season$`3PA`+(eighth_season$`3PA`*eighth_season$Position)+(eighth_season$Age*eighth_season$PTS)+(eighth_season$Age*eighth_season$Position)
,data=eighth_season)
fit8<-stepAIC(season_8,direction="both",k=2)

summary(season_8)

#plotting survival curve for injury occurring in the eighth season
survival_curve8<-plot(survfit(season_8), ylim=c(0,1),main="Survival Curve Season 8",xlab="Time",ylab="Survival Probaility")
survival_curve8

# Cox-Residuals for assessing model fit
coxres_8<-season_8$y[,2]-residuals(season_8)
coxres_season8<-survfit(Surv(coxres_8,season_8$y[,2])~1)
plot(coxres_season8,fun="cumhaz",bty="n",lwd=2,las=1,xlim=c(0,1.2),ylim=c(0,1.5),main="Cox-Residuals Season 8",xlab="Residual", ylab="Cumulative hazard")
abline(0, 1, col="red", lwd=2)


# Martingale Residuals
plot(season_8$linear.predictors,residuals(season_8),ylim=c(-2,2),pch=19,las=1, bty="n",col=5:6,main="Martingale Residuals Season 8",xlab="Prognostic Index", ylab="Martingale Residual")
abline(0,0,lty=2,lwd=2)
legend("bottomleft", c("Censored","Failures"),cex=0.8,col=5:6,pch=19)
```

Season 9
```{r}
# subsetting to only data in the ninth season
ninth_season<-subset(injurydata,injurydata$Season=="2019-2020")
ninth_season

# creating a dummy variable for censory indicator
z9=ifelse(ninth_season$`Censored Indicator`=="1",1,0)
z9

# running stepwise function on all covariates in ninth season
season_9<-coxph(Surv(ninth_season$`Minutes Before Injury`,z9)~ninth_season$FGA+ninth_season$FTA+ninth_season$REB
+ninth_season$`Number of Seasons Played`+ninth_season$FGM+ninth_season$FTM+
ninth_season$FTA+ninth_season$TOV+ninth_season$PF+ninth_season$AST
+ninth_season$STL+ninth_season$BLK+ninth_season$PTS+ninth_season$`Height cm`
+ninth_season$Weight+ninth_season$`3PA`+(ninth_season$`3PA`*ninth_season$Position)+(ninth_season$Age*ninth_season$PTS)+(ninth_season$Age*ninth_season$Position)
,data=ninth_season)
fit9<-stepAIC(season_9,direction="both",k=2)

summary(season_9)

#plotting survival curve for injury occurring in the ninth season
survival_curve9<-plot(survfit(season_9),xlim=c(0,100), ylim=c(0,1),main="Survival Curve Season 9")
survival_curve9

# Cox-Residuals for assessing model fit
coxres_9<-season_9$y[,2]-residuals(season_9)
coxres_season9<-survfit(Surv(coxres_9,season_9$y[,2])~1)
plot(coxres_season9,fun="cumhaz",bty="n",lwd=2,las=1,xlim=c(0,1.2),ylim=c(0,1.5),main="Cox-Residuals Season 9",xlab="Residual", ylab="Cumulative hazard")
abline(0, 1, col="red", lwd=2)

# Martingale Residuals
plot(season_9$linear.predictors,residuals(season_9),ylim=c(-2,2),pch=19,las=1, bty="n",col=5:6,main="Martingale Residuals Season 9",xlab="Prognostic Index", ylab="Martingale Residual")
abline(0,0,lty=2,lwd=2)
legend("bottomleft", c("Censored","Failures"),cex=0.8,col=5:6,pch=19)
```

Table indicating number of times each covariate was present in the lowest AIC model for each individual season
```{r}
freq<-matrix(c(7,4,3,3,9,6,4,4,5,1,4,2,1,4,5,3,7,6,2,1),ncol=20,byrow=FALSE)
colnames(freq)<-c("FGA","FGM", "FTA","FTM","3PA","PTS","REB","TOV","AST","STL",
                  "PF","BLK","Height","Weight","Age","Number of Seasons Played",
                  "Position","3PA:Position", "Age:PTS","Age:Position")
rownames(freq)<-c("Times Occurred")

freqtab<-as.table(freq)
freqtab
```


All Seasons
```{r}
all_seasons<-coxph(Surv(injurydata$`Minutes Before Injury`,injurydata$`Censory Indicator`)~injurydata$FGA+
injurydata$FTA+injurydata$REB
+injurydata$`Number of Seasons Played`+injurydata$FGM+injurydata$FTM+
injurydata$FTA+injurydata$TOV+injurydata$PF+injurydata$AST
+injurydata$STL+injurydata$BLK+injurydata$PTS+injurydata$`Height cm`
+injurydata$Weight+injurydata$`3PA`+(injurydata$`3PA`*injurydata$Position)+(injurydata$Age*injurydata$PTS)+(injurydata$Age*injurydata$Position)
,data=injurydata)

summary(all_seasons)


#plotting survival curve for injury occurring in the all seasons
survival_curveall<-plot(survfit(all_seasons), ylim=c(0,1),xlab="Time",ylab="Survival Probability",main="Survival Curve All Seasons")
survival_curveall

# Cox-Residuals for assessing model fit
coxres_all<-all_seasons$y[,2]-residuals(all_seasons)
coxres_allseasons<-survfit(Surv(coxres_all,all_seasons$y[,2])~1)
plot(coxres_allseasons,fun="cumhaz",bty="n",lwd=2,las=1,xlim=c(0,1.2),ylim=c(0,1.5),main="Cox-Residuals All Seasons",xlab="Residual", ylab="Cumulative hazard")
abline(0, 1, col="red", lwd=2)



# Martingale Residuals
plot(all_seasons$linear.predictors,residuals(all_seasons),ylim=c(-4,4),pch=19,las=1, bty="n",col=5:6,main="Martingale Residuals All Seasons",xlab="Time", ylab="Martingale Residual")
abline(0,0,lty=2,lwd=2)
legend("bottomleft", c("Censored","Failures"),cex=0.8,col=5:6,pch=19)

```

Removing the 2011-2012 Season because only 66 games were possible
```{r}
sinjurydata<-subset(injurydata,injurydata$Season!="2011-2012")
sinjurydata

wo_second<-coxph(Surv(sinjurydata$`Minutes Before Injury`,sinjurydata$`Censory Indicator`)~sinjurydata$FGA+
sinjurydata$FTA+sinjurydata$REB
+sinjurydata$`Number of Seasons Played`+sinjurydata$FGM+sinjurydata$FTM+
sinjurydata$FTA+sinjurydata$TOV+sinjurydata$PF+sinjurydata$AST
+sinjurydata$STL+sinjurydata$BLK+sinjurydata$PTS+sinjurydata$`Height cm`
+sinjurydata$Weight+sinjurydata$`3PA`+(sinjurydata$`3PA`*sinjurydata$Position)+(sinjurydata$Age*sinjurydata$PTS)+(sinjurydata$Age*sinjurydata$Position)
,data=sinjurydata)

summary(wo_second)

fitall<-stepAIC(wo_second,direction="both",k=2)

#plotting survival curve for injury occurring in the all seasons
survival_curvewo<-plot(survfit(wo_second), ylim=c(0,1),xlab="Time",ylab="Survival Probability",main="Survival Curve All Seasons")
survival_curvewo

# Cox-Residuals for assessing model fit
coxres_wo<-wo_second$y[,2]-residuals(wo_second)
coxres_wo_second<-survfit(Surv(coxres_wo,wo_second$y[,2])~1)
plot(coxres_wo_second,fun="cumhaz",bty="n",lwd=2,las=1,xlim=c(0,1.2),ylim=c(0,1.5),main="Cox-Residuals All Seasons",xlab="Residual", ylab="Cumulative hazard")
abline(0, 1, col="red", lwd=2)


# Martingale Residuals
plot(wo_second$linear.predictors,residuals(wo_second),ylim=c(-4,4),pch=19,las=1, bty="n",col=5:6,main="Martingale Residuals All Seasons",xlab="Time", ylab="Martingale Residual")
abline(0,0,lty=2,lwd=2)
legend("bottomleft", c("Censored","Failures"),cex=0.8,col=5:6,pch=19)

```


All Seasons using the stepAIC covariates from the previous model and removing the 2011-2012 Season
```{r}
sinjurydata<-subset(injurydata,injurydata$Season!="2011-2012")
sinjurydata

final_wosec<-coxph(Surv(sinjurydata$`Minutes Before Injury`,sinjurydata$`Censory Indicator`)~sinjurydata$FGA+
sinjurydata$REB
+sinjurydata$`Number of Seasons Played`+sinjurydata$FGM+
sinjurydata$PF+sinjurydata$AST+sinjurydata$STL
+sinjurydata$BLK+sinjurydata$`3PA`+sinjurydata$Position+sinjurydata$Age
,data=sinjurydata)

summary(final_wosec)

#plotting survival curve for injury occurring in the all seasons
survival_curvewo<-plot(survfit(final_wosec), ylim=c(0,1),xlab="Time",ylab="Survival Probability",main="Survival Curve Final Model")
survival_curvewo

# Cox-Residuals for assessing model fit
coxres_wo<-final_wosec$y[,2]-residuals(final_wosec)
coxres_wo_second<-survfit(Surv(coxres_wo,final_wosec$y[,2])~1)
plot(coxres_wo_second,fun="cumhaz",bty="n",lwd=2,las=1,xlim=c(0,1.2),ylim=c(0,1.5),main="Cox-Residuals Final Model",xlab="Residual", ylab="Cumulative hazard")
abline(0, 1, col="red", lwd=2)



# Martingale Residuals
plot(final_wosec$linear.predictors,residuals(final_wosec),ylim=c(-4,4),pch=19,las=1, bty="n",col=5:6,main="Martingale Residuals Final Model",xlab="Time", ylab="Martingale Residual")
abline(0,0,lty=2,lwd=2)
legend("bottomleft", c("Censored","Failures"),cex=0.8,col=5:6,pch=19)
```

